% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2018 Jason R. Blevins <jblevins@xbeta.org>
% https://jblevins.org/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

% Set your name here
\def\name{\textbf{Tzu-Ting Yang (楊子霆)}}

% Load packages
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem} % Enumerate with [resume] option
\usepackage{fontspec} % Requires XeTeX
\usepackage{sectsty} % Custom section fonts
\usepackage{xeCJK} % 讓中英文字體分開設置
% ---------- 字型 ----------
\setmainfont{Times New Roman}
\ifwindows
  \setCJKmainfont{PMingLiU}
  \newCJKfontfamily\heiti{Microsoft JhengHei}
\else
  \setCJKmainfont{Noto Serif CJK TC}
  \newCJKfontfamily\heiti{Noto Sans CJK TC}
\fi
%\setCJKmainfont{新細明體} %設定中文為系統上的字型,而英文不去更動,使用原TeX字型
%\usepackage[MnSymbol]{mathspec}
%\setmainfont{Minion Pro}
%\setmathfont[range=\mathup/{num,latin,Latin,greek,Greek}]{Minion Pro}
%\setmathfont[range=\mathbfup/{num,latin,Latin,greek,Greek}]{MinionPro-Bold}
%\setmathfont[range=\mathit/{num,latin,Latin,greek,Greek}]{MinionPro-It}
%\setmathfont[range=\mathbfit/{num,latin,Latin,greek,Greek}]{MinionPro-BoldIt}

%\setCJKmainfont{CWTEX}
%\setCJKfamilyfont{R}{CWTEX-R}
%\setmainfont[Numbers=OldStyle]{Minion Pro}
\XeTeXlinebreaklocale "zh"
\XeTeXlinebreakskip = 0pt plus 1pt %這兩行一定要加,中文才能自動換行
% Body
%\setmainfont{Garamond Premier Pro}

% Title
%\newfontfamily\titleface{Chaparral Pro Subhead}
\newcommand{\titlefont}[1]{{\titleface\large\MakeUppercase{#1}}}

% Section Headings
%\newfontfamily\sectionface{Chaparral Pro Subhead}
\sectionfont{\sectionface\mdseries\normalsize\uppercase}
\subsectionfont{\sectionface\mdseries\normalsize\itshape}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  pdfauthor = {\name},
  pdfkeywords = {economics, econometrics, empirical industrial organization,
    applied microeconomics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
      \setlength{\leftmargin}{1.5em}
      \setlength{\itemsep}{0.25em}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0.25em}
    }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.25em}

% Print the month and year
\renewcommand{\today}{\ifcase \month \or January\or February\or March\or April\or May%
\or June\or July\or August\or September\or October\or November\or December\fi%
\space \number \year}

\begin{document}

% Place name at left and date at right
\titlefont{\name}

% Alternatively, print name centered and bold:
%\centerline{\titlefont{\name}}

% Date
\bigskip
\today

% Contact Information
\bigskip
\begin{minipage}[t]{0.495\textwidth}
  Institute of Economics \\
  Academia Sinica \\
  308 Building B \\
  128 Academia Road, Section 2 \\
  Taipei, Taiwan
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Phone: 886-2782-2791 \\
  Fax: 886-2782-2791 \\
  Office: 308 Building B \\
  Email: \href{mailto:ttyang@econ.sinica.edu.tw}{ttyang@econ.sinica.edu.tw} \\
  Homepage: \href{https://sites.google.com/view/cpelab/}{https://sites.google.com/view/cpelab/}
\end{minipage}

\section*{\textbf{Full-Time Faculty Positions}}

\begin{itemize}
\item Institute of Economics, Academia Sinica
  \begin{itemize}
  	  \item Associate Research Fellow, 2021--present.
  \item Assistant Research Fellow, 2015--2021.
  %\item Assistant Professor, 2010--2017.
  \end{itemize}
\end{itemize}
\section*{\textbf{Joint Appointment \& Adjunct Faculty Positions}}
\begin{itemize}
\item Department of Agricultural Economics, National Taiwan University
\begin{itemize}
	\item Associate Professor, 2023--present
\end{itemize}		
		
\item IMES program, National Chengchi University
\begin{itemize}
	\item Associate Professor, 2021--present
	\item Assistant Professor, 2017--2021
\end{itemize}	
	
\item Department of Economics, National Taiwan University
\begin{itemize}
	\item Associate Professor, 2021--present.
	\item Assistant Professor, 2019--2021.
	%\item Assistant Professor, 2010--2017.
\end{itemize}


\end{itemize}

% \subsection*{Duke University, Department of Economics}
%
% \begin{itemize}
% \item Research Assistant, Jacob Vigdor, Summer 2005--Summer 2006.
% \item Teaching Assistant, Ph.D. Microeconomic Analysis, Thomas Nechyba, Fall 2005.
% \item Teaching Assistant, Ph.D. Game Theory, Curtis Taylor, Spring 2006.
% \item Instructor, Microeconomics Qualifier Camp, Summer 2006.
% \item Research Assistant, Han Hong, Fall 2006--Spring 2007.
% \item Research Assistant, Aprajit Mahajan and Alessandro Tarozzi,
%   October--November 2006, March--June 2007.
% \item Research Assistant, Shakeeb Khan and Christopher Timmins,
%   March--June 2007.
% \item Teaching Assistant, Ph.D. Econometrics II, Shakeeb Khan,
%   Spring 2007.
% \item Research Assistant, Peter Arcidiacono, Patrick Bayer,
%   and Paul Ellickson, Fall 2007--Spring 2009.
% \item Research Assistant, Shakeeb Khan, Fall 2009--Spring 2010.
% \item Research Assistant, Aprajit Mahajan, July--September 2009.
% \end{itemize}

% \subsection*{North Carolina State University, Department of Mathematics}
%
% \begin{itemize}
% \item Research Assistant, Moody Chu and Robert Funderlic,
%   Spring 2003--Fall 2004.
% \item Mathematics Tutor, Academic Support Program for Student Athletes,
%   Summer 2001.
% \end{itemize}

% \subsection*{Colorado School of Mines,
%   Department of Mathematical and Computer Sciences}
%
% \begin{itemize}
% \item Research Assistant, Willy Hereman, Summer 2002.
% \end{itemize}

\section*{\textbf{Education}}

\begin{itemize}
  \item Ph.D. in Economics, University of British Columbia, 2010 - 2015
    % Received May 16, 2010
    %\begin{itemize}
    %\item Dissertation Title: ``Essays in Industrial Organization and Econometrics''.
    %\item Committee: Han Hong (co-chair), Shakeeb Khan (co-chair), Paul Ellickson, Andrew Sweeting.
    %\item Institute on Computational Economics Fellow, University of Chicago, 2006.
    %\end{itemize}
  \item M.A. in Economics, National Taiwan University, 2006 - 2008
    % Received May 14, 2006
  \item B.A. in Political Science, National Taiwan University, 2002 - 2006
    % Received May 14, 2004
    %\begin{itemize}
    %\item Phi Beta Kappa, Zeta of North Carolina, 2003.
    %\item Budapest Semesters in Mathematics, Fall 2002.
    %\item NSF Research Experiences for Undergraduates, Colorado School of Mines, 2002.
    %\end{itemize}
\end{itemize}

\section*{\textbf{Research Interests}}

Applied Micro, Labor Economics, Health Economics and Public Economics

\section*{\textbf{Publications}}

\begin{enumerate}
%\begin{itemize}




\item
\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4300448}{The Effect of Financial Resources on Fertility: Evidence from Administrative Data on Lottery Winners} \textit{\textbf{Journal of Labor Economics}}, \textit{forthcoming} (with Yung-Yu Tsai, Hsing-Wen Han and Kuang-Ta Lo).

\item
\href{https://www.dropbox.com/scl/fi/xigzri0wajwxznqpplb4c/Dynamics-and-Sources-of-Wage-Inequality-in-Taiwan-Evidence-from-Employer-Employee-Matched-Data.pdf?rlkey=6jwpdl3vgwgk82z9q75s9cgg3&dl=0}{Dynamics and Sources of Wage Inequality in Taiwan: Evidence from Employer-Employee Matched Data} \textit{\textbf{Economic Inquiry}}, \textit{forthcoming} (with Huei-Ming Chen, Hsien-Ming Lien, and Po-Chun Huang).

\item
\href{https://www.sciencedirect.com/science/article/abs/pii/S0304387825000112}{Parental Responses to Child Disability: Gender Differences and Relative Earnings} \textit{\textbf{Journal of Development Economics}}, 2025 (with Kamhon Kan and T. Terry Cheung).

\item
\href{https://www.sciencedirect.com/science/article/abs/pii/S0378426624002929}{Windfall Gains and Stock Market Participation Evidence from Shopping Receipt Lottery} \textit{\textbf{Journal of Banking and Finance}}, 2025 (with Tzu-Chang Forrest Cheng, Hsuan-Hua Huang, Tse-Chun Lin and Jian-Da Zhu).


\item
\href{https://www.dropbox.com/scl/fi/l9acw3h4gj8yzrdfav2w5/Job-Loss_Health_Full_v2.pdf?rlkey=bkgdf6v72teahl6jj4iq7b440&dl=0}{Long-term Effects of Job Displacement on Earnings and Mental health: Evidence from Population-wide Administrative Data} \textit{\textbf{Economics Letters}}, 111688, 2024 (with Yung-Yu Tsai and Po-Chun Huang).

\item
\href{https://www.dropbox.com/s/lz3pqw0rozyn68r/knowing_taiwan_ver_2017_08_tzu_ting_v58.pdf?dl=0}{Curriculum and National Identity: Evidence from the 1997 Curriculum Reform in Taiwan} \textit{\textbf{Journal of Development Economics}}, 163, 103078, 2023 (with Wei-Lin Chen and Ming-Jen Lin).

\item
\href{https://doi.org/10.1371/journal.pone.0271810}{Measuring voluntary responses in healthcare utilization during the COVID-19 pandemic: Evidence from Taiwan}  \textit{\textbf{PLOS ONE}}, 17(12): e0271810, 2022 (with Yung-Yu Tsai). :contentReference[oaicite:1]{index=1}


\item
\href{https://www.dropbox.com/s/etfzl98k6d83ef5/Spontaneous_Population_Mobility_v23.pdf?dl=0}{JUE Insight: Demand for Transportation and Spatial Pattern of Economic Activity during the Pandemic} \textit{\textbf{Journal of Urban Economics}},127, 103426, 2022 (with Kong-Pin Chen and Jui-Chung Yang).

\item
\href{https://www.dropbox.com/s/4bmmsvl2mko0thu/Optimal_UI_Tzu_Ting_v142.pdf?dl=0}{The Welfare Effects of Extending Unemployment Benefits: Evidence from Re-­employment and Unemployment Transfers} \textit{\textbf{Journal of Public Economics}}, 202 104500, 2021 (with Po-Chun Huang).

\item \href{https://www.dropbox.com/s/pe5n9a74avtwk6v/Children_copay_v176_parametric.pdf?dl=0}{Patient Cost-Sharing and Healthcare Utilization in Early Childhood: Evidence from a Regression Discontinuity Design}.
\textit{\textbf{American Economics Journal: Economic Policy}}, 12(3) 238-278, 2020 (with Hsing-Wen Han and Hsien-Ming Lien).

\item
\href{https://www.dropbox.com/s/i792d6jutss65b2/Proposal_pension_saving_JRI_v91_final.pdf?dl=0}{The Effect of Workplace Pensions on Household Saving: Evidence from a Natural Experiment in Taiwan}.
\textit{\textbf{Journal of Risk and Insurance}}, 87(1) 173-194, 2020.

\item \href{http://jhr.uwpress.org/content/early/2017/03/01/jhr.53.2.0115-6857R1.abstract}{Family Labor Supply and the Timing of Cash Transfers: Evidence from the Earned Income Tax Credit}.
\textit{\textbf{Journal of Human Resources}} 53(2) 445-473, 2018.

\item
\href{https://www.dropbox.com/s/z5b267cu72o6xlg/tot_wage_v63_olo_revised.pdf?dl=0}{Tax Audit and Tax Evasion: Evidence from Taiwanese Firms}. \textit{\textbf{Academia Economic Paper }}, \textit{forthcoming}, 2020 (with Yu-Chun Cheng, Hsing-Wen Han).


\item
\href{http://www.econ.ntu.edu.tw/ter/new/data/new/forthcoming/108-015.pdf}{Wealth Distribution in Taiwan 2004–2014: Evidence from the Individual Wealth Register Data}. \textit{\textbf{Taiwan Economic Review}}, \textit{forthcoming}, 2020 (with Hsing-Wen Han, Hsien-Ming Lien, Kuang-Ta Lo, Chung-Hsin Tseng).

\item
\href{https://www.dropbox.com/s/z5b267cu72o6xlg/tot_wage_v63_olo_revised.pdf?dl=0}{Decoupling of Wage Growth and Productivity Growth in Taiwan: An Empirical Investigation}. \textit{\textbf{Academia Economic Paper}} 46(2) 263-322, 2018 (with Yi-Ling Lin).   
\item \href{http://www.econ.sinica.edu.tw/UpFiles/2013090214141704234/Periodicals_Pdf2013090215152407682/aep37-3-3.pdf}{Who Pays Pensions? The Impact of New Labor Pension Scheme on Labor Wages}.
  \textit{\textbf{Academia Economic Paper}} 37, 339-368, 2009 (with Ming-Ching Luoh).



\end{enumerate}
%\end{itemize}


%\section*{Other Publications}

%\begin{enumerate}[resume]
%\item Blevins, J.~R. (2009).
 % \href{https://jblevins.org/research/generic-list}{A Generic Linked List Implementation in Fortran 95}.
  %\textit{ACM Fortran Forum} 28(3), 2--7.
%\end{enumerate}

%\section*{\textbf{Working Papers}}

%\begin{enumerate}[resume]
%\begin{itemize}	

%\item
 % \href{https://www.dropbox.com/s/sv4gaqpfk53n5a2/optimal_ui_tzu_ting_v53.pdf?dl=0}{An Evaluation of Optimal Unemployment Insurance Using Two Natural Experiments } (with Po-Chun Huang).




%\href{}{The Effect of Compensation on Employee Turnover: Evidence from Taiwanese Administrative Data} (with Hsing-Wen Han, Yu-Chun Cheng, Hao-Chung Li, and Wen-Chieh Lee).

 
%\end{itemize}
%\end{enumerate}



 
 
% \end{enumerate}



\section*{\textbf{Awards}}

\begin{itemize}
	\item Chao-Nan Chen Memorial Award (台灣經濟學會陳昭南院士紀念獎), 2025
    \item 	Outstanding Research Award from National Science and Technology Council (國家科學及技術委員會傑出研究獎), 2024
	\item Young Scholar Research Award from Taiwan Risk and Insurance Association (台灣風險與管理學會年輕學者研究獎), 2024
		\item Outstanding Paper Award from Taiwan Economic Association (台灣經濟學會傑出論文獎), 2024
	\item Sun Yun-suan Academic Award from Sun Yun-suan Foundation (孫運璿基金會最佳論文獎), 2023
	\item Young Scholar Award from Taiwan Econometric Society (台灣計量經濟學會年輕學者獎), 2023
	\item Outstanding Teaching Award from National Taiwan University (國立台灣大學教學優良獎), 2023	
	\item Outstanding Faculty Research Scholarship from Academia Sinica (中央研究院學術研究獎金), 2023
	\item Outstanding Teaching Award from National Taiwan University (國立台灣大學教學優良獎), 2022
	\item Outstanding Faculty Research Scholarship from Academia Sinica (中央研究院學術研究獎金), 2022
	\item Early-Career Investigator Research Achievement Award (中研院年輕學者研究成果獎), 2022		
	\item Outstanding Paper Award from Taiwan Economic Association (台灣經濟學會傑出論文獎), 2021
	\item Ta-You Wu Memorial Award from Ministry of Science and Technology (科技部吳大猷先生紀念獎), 2021
	\item Outstanding Teaching Award from National Taiwan University (國立台灣大學教學優良獎), 2021
	\item Outstanding Faculty Research Scholarship from Academia Sinica (中央研究院學術研究獎金), 2021
	\item Outstanding Paper Award from Taiwan Economic Association (台灣經濟學會傑出論文獎), 2020
	\item Outstanding Faculty Research Scholarship from Academia Sinica (中央研究院學術研究獎金), 2020
\end{itemize}


% \subsection*{Scientific Software}
%
% \begin{itemize}
% \item \href{https://jblevins.org/research/pdest}{PDESolutionTester},
%   A Mathematica program for the symbolic verification of exact solutions
%   of nonlinear partial differential equations,
%   with Jeff Heath and Willy Hereman (2002).
% \item \href{https://jblevins.org/research/dfbr}{DFBR},
%   A Stata program for distribution-free estimation of heteroskedastic
%   binary response models,
%   with Shakeeb Khan (2009).
% \end{itemize}




\section*{\textbf{Peer Review}}

Reviewer for
\textit{American Economic Review}, \textit{Proceedings of the National Academy of Sciences}, \textit{Journal of Public Economics}, \textit{Economic Journal}, \textit{Journal of Health Economics}, \textit{Journal of Development Economics}, \textit{Journal of Population Economics},  \textit{Journal of Applied Econometrics}, \textit{Labour Economics}, \textit{Health Economics}, \textit{Journal of Policy Analysis and Management} \textit{National Tax Journal}, \textit{Demography},
\textit{Economic Inquiry}, \textit{Journal of Economic Behavior \& Organization},  \textit{Journal of Regional Science}, 
\textit{Pacific Economic Review},
\textit{Economics Bulletin}, \textit{Food Policy}, \textit{Climate Change Economics},
\textit{經濟論文},
\textit{經濟論文叢刊},\textit{人文及社會科學集刊}


\section*{\textbf{Editorial Broad}}

\begin{itemize}
	\item Academia Economic Papers (經濟論文)
	\item Taiwan Economic Forecast and Policy (臺灣經濟預測與政策)
	\item Taiwan Economic Review (經濟論文叢刊)
	
\end{itemize}

\section*{\textbf{Academic and Administrative Service}}

\begin{itemize}
  \item Institute Representative, Academia Sinica (中央研究院院務代表), 2025--2027.
  
  \item Member, Institutional Review Board / Research Ethics Committee, Academia Sinica  
  (中央研究院醫學倫理委員會委員), 2018--present.
  
  \item Member, Academic Affairs Committee,  
  Institute of Economics, Academia Sinica  
  (中央研究院經濟研究所學術事務委員會委員).
  
  \item Member and Executive Secretary, Faculty Search Committee,  
  Institute of Economics, Academia Sinica  
  (中央研究院經濟研究所新聘委員會委員暨執行秘書).
  
  \item Member, Academic Seminar Committee,  
  Institute of Economics, Academia Sinica  
  (中央研究院經濟研究所學術研討會委員).
  
  \item Member, Editorial Committee, Taiwan Economic Association  
  (台灣經濟學會編輯委員會委員).
  
  \item Board Member, Taiwan Population Association  
  (台灣人口學會理事).
  
  \item Board Member, Taiwan Econometric Society  
  (台灣經濟計量學會理事).
  
  \item Deputy Secretary General, Taiwan Health Economics Association  
  (台灣健康經濟學會副秘書長).
  
  \item Committee Member, National Health Insurance Global Budget Review Committee,  
  National Development Council  
  (國家發展委員會全民健康保險總額審議委員).
  
  \item Committee Member, National Health Insurance Global Budget Review Committee,  
  Ministry of Health and Welfare  
  (衛生福利部全民健康保險總額審議委員).
  
  \item Committee Member, Labor Policy Review Panel, Ministry of Labor  
  (勞動部勞動政策議題審議委員).
  
  \item Advisory Committee Member, Drug Pricing for Innovative Pharmaceuticals,  
  National Health Insurance Administration, Ministry of Health and Welfare  
  (健保署臺灣首發新藥核價諮詢委員).
\end{itemize}




\section*{\textbf{Teaching}}

\subsection*{National Chengchi University}

\begin{itemize}
\item Causal Inference and Data Science in Economics (Ph.D./M.A.):
  \href{https://causaldatalab.wordpress.com/teaching/}{Spring 2018, Spring 2019, Spring 2020, Spring 2021, Spring 2022, Spring 2023, Spring 2024}. % 5 students, 5 quarter 
\item Causal Inference and Big Data (M.A.):
  \href{https://causaldatalab.wordpress.com/2017/02/24/causal-inference-and-big-data-spring-2017/}{Spring 2017}. % 47 students, 5 
\end{itemize}


\subsection*{National Taiwan University}

\begin{itemize}
	\item Topics in Labor Economics: Empirical Methods and Applications  (Ph.D./M.A./B.A.):
	\href{https://sites.google.com/view/cpelab/teaching?authuser=0}{Spring 2019, Spring 2020, Spring 2021, Spring 2022, Spring 2023, Spring 2024}. % 5 students, 5 quarter 
	\item Applied Microeconomics  (Ph.D./M.A.):
	\href{https://sites.google.com/view/cpelab/teaching?authuser=0}{Spring 2020, Fall 2020, Spring 2021, Fall 2021}.
		\item Applied Econometrics  (Ph.D./M.A.):
	\href{https://causaldatalab.wordpress.com/teaching/}{Fall 2023}.

	
\end{itemize}


\end{document}

%%% Local Variables: 
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% End: 